Ribosome accumulation during early phase resistance training

### 2021-12-07 manuscript.Rmd
update after internal revision

---
title: "Ribosome accumulation during early phase resistance training"
author:
  - Daniel Hammarström^1,2,£^*
  - Sjur J. Øfsteng^2,£^
  - Nicolai B. Jacobsen^1^
  - Krister B. Flobergseter^1^
  - Bent R. Rønnestad^1^
  - Stian Ellefsen^1,3^
date: ''
output:
  pdf_document:
    latex_engine: xelatex
  word_document:
    reference_docx: resources/manuscript_word_template.docx
csl: resources/experimental-physiology.csl
bibliography: resources/bibliography.bib
header-includes: 
  \usepackage{wasysym}
editor_options:
  chunk_output_type: console
---
<!-- This is a comment  -->
<!-- Add comments after each reference for tracking (eg[@RN2364]<!-- comment -->
<!-- After references, add a row break without space (this will put the reference on the end on the line). -->

>>>>

---
title: "Ribosome accumulation during early phase resistance training"
author:
  - Daniel Hammarström^1,2,£^*
  - Sjur J. Øfsteng^2,£^
  - Nicolai B. Jacobsen^1^
  - Krister B. Flobergseter^1^
  - Bent R. Rønnestad^1^
  - Stian Ellefsen^1,3^
date: ''
output:
  pdf_document:
    latex_engine: xelatex
  word_document:
    reference_docx: resources/manuscript_word_template.docx
csl: resources/acta-physiologica.csl
bibliography: resources/bibliography.bib
header-includes: 
  \usepackage{wasysym}
editor_options:
  chunk_output_type: console
---
<!-- This is a comment  -->
<!-- Add comments after each reference for tracking (eg[@RN2364]<!-- comment -->
<!-- After references, add a row break without space (this will put the reference on the end on the line). -->
